Effect of quality-adjusted production function inputs

### 2015-06-22 Articles/Presentation_ESEE_2015/ESEE_2015.Rnw
Streamlined code for fittedAndResidData.

<<Fitted_and_Residuals>>=
fittedAndResidData <- function(model){
  df <- data.frame(select(getData(model), Year))
  # Trim fitted to be same length as df to eliminate problems with possible NAs at end of fitted
  df$fitted <- yhat(model)[c(1:length(df$Year))]
  df$Residuals <- resid(model)[c(1:length(df$Year))]
  return(df)  
}

temp_data <- leaf_apply(models, class=c("CDEmodel", "cesModel", "LINEXmodel"), f = function(model, id){
  df <- fittedAndResidData(model)
  f <- model$formula
  response <- summands(f, right = FALSE)
  df[[response]] <- getData(model)[[response]] # Add iGDP to the data frame
  id_list <- strsplit(id, split = "[.]")[[1]]
  df$Country <- id_list[[1]]
  df$flavor <- if (id_list[[2]] == "unadjusted") "Unadjusted" else "Quality-adjusted"
  df$energy <- if (id_list[[3]] == "noE") "Without energy" else "With energy"
  df$model <- id_list[[4]]
  df$nest <- if (length(id_list) > 4) id_list[[5]] else NA
  return(df)  
}) %>% do.call(rbind, .)

>>>>

<<Fitted_and_Residuals>>=
fittedAndResidData <- function(model, id){
  df <- data.frame(select(getData(model), Year))
  # Trim fitted to be same length as df to eliminate problems with possible NAs at end of fitted
  df$fitted <- yhat(model)[c(1:length(df$Year))]
  df$Residuals <- resid(model)[c(1:length(df$Year))]
  df <- na.omit(df)
  # Now add the response, using the original variable name.
  df[[summands(model$formula, right = FALSE)]] <- response(model)
  # Now add meta information
  id_list <- strsplit(id, split = "[.]")[[1]]
  df$Country <- id_list[[1]]
  df$flavor <- if (id_list[[2]] == "unadjusted") "Unadjusted" else "Quality-adjusted"
  df$energy <- if (id_list[[3]] == "noE") "Without energy" else "With energy"
  df$model <- id_list[[4]]
  df$nest <- if (length(id_list) > 4) id_list[[5]] else NA
  return(df)  
}

temp_data <- leaf_apply(models, class=c("CDEmodel", "cesModel", "LINEXmodel"), f = function(model, id){
  return(fittedAndResidData(model, id))  
}) %>% do.call(rbind, .)
temp_data$cst <- FALSE

# temp_data_CST <- leaf_apply(modelsCST,class=c("plm", "lm"), f = function(model, id){
#   return(fittedAndResidData(model, id))
# }) %>% do.call(rbind, .)
# temp_data_CST$cst <- TRUE
